---
title: "Untitled"
author: "putin"
date: "November 19, 2018"
output:
  html_document:
    df_print: kable
    fig_caption: yes
    number_sections: yes
    theme: journal
    toc: yes
    toc_float: yes
  html_notebook:
    fig_height: 3.25
    fig_width: 3.25
    number_sections: yes
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
---


# Intro
```{r imports, echo=F, message=F, warning=F}
library(ggplot2)
#library(ggExtra)
#library(cowplot)
#library(ggpubr)

library(dplyr)
library(tidyr)
library(readxl)
```
```{r get_data, echo=F, message=F, warning=F}
setwd("~/Desktop/politics1")
#setwd("C:/Users/CalzzOne/Google Drive/Licente/0Acu/Alexandra Dardalat/")
baza_de_date <- read_excel("politics1.xlsx")
#View(baza_de_date)
labels <- names(baza_de_date)
baza_de_date$Winner <- factor(baza_de_date$Winner, levels=c("Republican", "Democrat"))
#baza_de_date$`AT1 Polymorphism` <- factor(baza_de_date$`AT1 Polymorphism`, levels=c("AC", "CC", "AA"))


```
```{r split_violin, echo=F, message=F, warning=F}
GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, 
                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
                             data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
                             grp <- data[1, "group"]
                             newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
                             newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
                             newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
                             
                             if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
                               stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
                                                                         1))
                               quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
                               aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
                               aesthetics$alpha <- rep(1, nrow(quantiles))
                               both <- cbind(quantiles, aesthetics)
                               quantile_grob <- GeomPath$draw_panel(both, ...)
                               ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
                             }
                             else {
                               ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
                             }
                           })

geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., 
                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, 
                              show.legend = NA, inherit.aes = TRUE) {
  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, 
        position = position, show.legend = show.legend, inherit.aes = inherit.aes, 
        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
}
```
```{r prepare, echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
x = "Winner"
y = c("Democrat %", "Republican %")
df <- baza_de_date %>% 
  dplyr::select(c(x, y)) %>%
  tidyr::gather(variable, value, -x)
```

# Regular
## theme_gray / theme_grey
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  theme_grey()+
  labs(title="theme_grey", subtitle="ggplot2",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_bw
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  theme_bw()+
  labs(title="theme_bw", subtitle="ggplot2",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_classic
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  theme_classic()+
  labs(title="theme_classic", subtitle="ggplot2",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_dark
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  theme_dark() +
  labs(title="theme_dark", subtitle="ggplot2",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```


## theme_light
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  theme_light() +
  labs(title="theme_light", subtitle="ggplot2",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_linedraw
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  theme_linedraw() +
  labs(title="theme_linedraw", subtitle="ggplot2",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```


## theme_minimal
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  theme_minimal() +
  labs(title="theme_minimal", subtitle="ggplot2",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_test
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  theme_test() +
  labs(title="theme_test", subtitle="ggplot2",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

# ggpubr
## theme_classic2
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggpubr::theme_classic2() +
  labs(title="theme_classic2", subtitle="ggpubr",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_cleveland
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggpubr::theme_cleveland() +
  labs(title="theme_cleveland", subtitle="ggpubr",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_pubclean
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggpubr::theme_pubclean() +
  labs(title="theme_pubclean", subtitle="ggpubr",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_pubr
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggpubr::theme_pubr() +
  labs(title="theme_pubr", subtitle="ggpubr",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_transparent
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggpubr::theme_transparent() +
  labs(title="theme_transparent", subtitle="ggpubr",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

# cowplot

## theme_cowplot
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  cowplot::theme_cowplot() +
  labs(title="theme_cowplot", subtitle="cowplot",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_map
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  cowplot::theme_map() +
  labs(title="theme_map", subtitle="cowplot",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_nothing
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  cowplot::theme_nothing() + 
  labs(title="theme_nothing", subtitle="cowplot",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```




# ggthemes

## theme_base
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_base() +
  labs(title="theme_base", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_calc
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_calc() +
  labs(title="theme_calc", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_economist
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_economist() +
  labs(title="theme_economist", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_economist_white
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_economist_white() +
  labs(title="theme_economist_white", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_excel
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_excel() +
  labs(title="theme_excel", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_excel
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_excel() +
  labs(title="theme_excel_new", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_few
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_few() +
  labs(title="theme_few", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_fivethirtyeight
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_fivethirtyeight() +
  labs(title="theme_fivethirtyeight", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_foundation
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_foundation() +
  labs(title="theme_foundation", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_gdocs
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_gdocs() +
  labs(title="theme_gdocs", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_hc
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_hc() +
  labs(title="theme_hc", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_igray
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_igray() +
  labs(title="theme_igray", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_map
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_map() +
  labs(title="theme_map", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_pander
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_pander() +
  labs(title="theme_pander", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_par
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_par() +
  labs(title="theme_par", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_solarized
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_solarized() +
  labs(title="theme_solarized", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_solarized
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_solarized_2() +
  labs(title="theme_solarized_2", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_solid
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_solid() +
  labs(title="theme_solid", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_stata
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_stata() +
  labs(title="theme_stata", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_tufte
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_tufte() +
  labs(title="theme_tufte", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

## theme_wsj
```{r echo=F, message=F, warning=F, fig.height=4, fig.width=4, dpi=144}
g3 <- ggplot(df) + aes(fill=Winner, y=value, x=variable) +
  ggthemes::theme_wsj() +
  labs(title="theme_wsj", subtitle="ggthemes",
       caption = "caption", tag = "a") +
  geom_split_violin(alpha=0.25) +
  geom_boxplot(alpha=0.75, width=0.25, varwidth = T) +
  geom_rug(aes(color=Winner), alpha=0.5,sides = "lr")+
  stat_summary(fun.y=mean, colour="black", geom="point", shape=18, size=3) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     name="% of votes received") + 
  theme(legend.position = "top") +
  theme(axis.title.x = element_blank())

plot(g3)
```

